Case 4

### 2017-05-11 EU-Circle/eu-circle_case-study-1.Rmd
EU-Circle cast 4

>>>>

## Wildfire risk

The fire season: May-October (allowing for longer season in the future).

Hazards: Smoke (Area/density) and burned area. Use historic data or model results (RCM)? Damage functions - has not been used and need to come up with some sensible choices (e.g. mean/minimum density of assets?). The assets are distributed unevenly (roads and power lines). Model risk in a conditioned Monte-Carlo type of fashion?

Data: number of events $n_f$, burned area $A_f$, area of smoke $A_s$, location of event $(x,y)$, the day of the event, number of multiple events $n_i\ i =[2,3,..]$.

### Fire indices

Gridded data which can be downscaled.

### Events

Model number of evens $n_f$ and their area $A_f$ seperately, a little like precipitation ($\mu$ and $f_w$). The area has an impact on the risk of affecting the number of assets. Base this on historic data and relate to large-scale conditions (predictors). Model as a partly stochastic process where the likelihood depends on an external variable. Poisson model (`GLM`) of $n_f$ and the nature of the $A_f$ distribution dictates the model strategy for the area.

Also model number of simultaneous events, which strain the fire fighters, as they need to split/divert resources. Based on historic data and the assumption of a Poisson process dependent on external condition.

### 2017-05-11 EU-Circle/eu-circle_case-study-2.Rmd
EU-Circle cast 4

```{r,warning=FALSE}
if (!file.exists('eu-circle_case-study-2_slp.rda')) {
  x <- retrieve('pp_0.25deg_reg.nc',path='~/storeB/data/data.ECAD',
                lon=c(10,30),lat=c(53,66))
  save(file='eu-circle_case-study-2_slp.rda',x)
} else load('eu-circle_case-study-2_slp.rda')
## Only keep the ECAD data
map(x,FUN='q95',new=FALSE)
```

>>>>

```{r,warning=FALSE,eval=FALSE}
if (!file.exists('eu-circle_case-study-2_slp.rda')) {
  x <- retrieve('pp_0.25deg_reg.nc',path='~/storeB/data/data.ECAD',
                lon=c(10,30),lat=c(53,66))
  save(file='eu-circle_case-study-2_slp.rda',x)
} else load('eu-circle_case-study-2_slp.rda')
## Only keep the ECAD data
map(x,FUN='q95',new=FALSE)
```

### 2017-05-11 EU-Circle/eu-circle_case-study-4.Rmd
EU-Circle cast 4

Bangladesh is highly vulnerable to climate induced hazrds and disasters and its coastal part are mostly threatened for the impacts of climate change in case of cyclone, storm surges, flood, salinity and tsunami disaster. Even last twenty years the coastal peoples have suffered due to super cyclone SIDR and AILA devastations. Last two deacdes a lots of disaster coping interventions have been provided to the community to achieve resiliency in this areas. So really it will be a field laboratory for the research of Disaster Resilience and Climate Change: Science and innovation for adaptation to climate  change: from assessing costs, risks and opportunities to demonstration of options and practices.

@@

>>>>

Bangladesh is highly vulnerable to climate induced hazrds and disasters and its coastal part are mostly threatened for the impacts of climate change in case of cyclone, storm surges, flood, salinity and tsunami disaster. Even last twenty years the coastal peoples have suffered due to super cyclone SIDR (2007-11-15) and AILA (YYYY-MM-DD) devastations. Last two deacdes a lots of disaster coping interventions have been provided to the community to achieve resiliency in this areas. So really it will be a field laboratory for the research of Disaster Resilience and Climate Change: Science and innovation for adaptation to climate  change: from assessing costs, risks and opportunities to demonstration of options and practices.

@@

## HURDAT2

```{r}
url <- 'http://www.aoml.noaa.gov/hrd/hurdat/hurdat2-1851-2016-apr2017.txt'

```
